Complex Analysis of Askaryan Radiation: UHE-$\nu$ Identification and Reconstruction via the Hilbert Envelope of Observed Signals

### 2025-08-15 template.tex
added efficiency figure and text

\item To illustrate the accuracy and efficiency of the model, Eq. \ref{eq:final}-\ref{eq:final2} and \ref{eq:final3}, are shown in Fig. \ref{fig:fig1}.

@@

@@

\end{itemize}

>>>>

\item To illustrate the accuracy of the model, Eqs. \ref{eq:final}-\ref{eq:final2} and \ref{eq:final3}, are shown in Fig. \ref{fig:fig1}.
\begin{figure}[ht]

@@

\begin{figure}[ht]

@@

\item A Monte Carlo data set was generated using NuRadioMC for UHE-$\nu$ interactions in a cylindrical ice volume with a depth of 0.65 km and a radius of 0.850 km.  The UHE-$\nu$ energies ranged from 10-100 PeV, with roughly equal numbers of UHE-$\nu$ in each 10 PeV bin.  The detector included a single string of 8 RF dipole antennas, a filtered passpand of [80,1000] MHz, and 256 samples per channel at a 1 GHz sampling rate.  The RF trigger responded when 3 of the 8 voltage traces exceeded $\pm 3$ times the $v_{\rm rms}$ of the thermal noise within 256 ns.  For each triggered UHE-$\nu$ interaction, the Hilbert envelope of the coherently summed waveform (CSW) was calculated and correlated against Eqs. \ref{eq:final}-\ref{eq:final2}.  A quick optimization over the whole data set yielded 0.15 GHz and 0.025 GHz for the $f_0$ and $\gamma$ parameters, respectively.  Each individual correlation was maximized by varying the just the $\sigma_t$ parameter, yielding an optimized analytical envelope for each event.  A thermal noise waveform reflective of the detector properties was also generated using NuRadioMC tools for each UHE-$\nu$ event.  The noise waveform was also correlated against the optimized analytical envelope.  The probability distributions for the correlation coefficients are shown in Fig. \ref{fig:fig3}.
\includegraphics[width=0.5\textwidth,trim=3.25cm 8.25cm 4.5cm 9.0cm,clip=true]{Aug15_plot1.pdf}
\caption{\label{fig:fig3} (Black circles) Noise distribution. (Gray dashed line) Fitting function to noise distribution.  (Solid black line) Exponential fit to tail of noise distribution.  (Solid gray line) UHE-$\nu$ signal distribution.  (Dashed black line) Optimized correlation coefficient threshold value.}
In Fig. \ref{fig:fig3}, the black circles represent the normalized histogram of the correlation coefficent between the optimized analytic envelope and the thermal noise waveform.  A function of the form $x^2 \exp(-0.5 x^2)$ was fit to the black circles on the interval [0.1,1.0], and is represented by the gray dashed line.  A function of the form $exp(-x)$ was fit to the noise distribution on the interval [0.28,1] to capture the limiting behavior, and is represented by the solid black line.  The solid gray line represents the signal distribution, which peaks at a correlation value of 0.96.  The vertical black dashed line represents a threshold value, 0.438.  For the simulated UHE-$\nu$ sample, 92\% of CSWs meet or exceed this correlation value when fit to an optimized analytic envelope.  Assuming the solid black line correctly describes the tail of the probability distribution function for noise correlation, a threshold of 0.438 is equivalent to 0.95 noise events per detector over a period of 5 years, at a noise trigger rate of 1 Hz.

Correlation vs SNR
\end{itemize}
